Qualifying Examination Paper

### 2018-10-18 main.tex
181018-0913 sync

Wtihin the theme of semantic learning and generation, several significant contributions were made during 2016 and 2017.  Pathak, Krahenbuhl, Donahue, Darrell, and Efros successfully used an adversarial approach to inpaint (fill in missing portions of) images with large extents of missing pixel data.  Their architecture was based on an encoder-decoder (TBD ref) combined with GAN.  In their approach, the encoder encodes both whole and masked (portions missing) images and $D$ tries to discriminate whole vs. masked, while $G$ generates the completed images, conditioned on the context. ...

 serves as $G$, attempting to reconstruct the context encoding from images with missing portions and the decoder feeds $D$ which tries to distinguish between reconstructed images and complete images.  Interestingly, and in contrast with \cite{mirza2014conditional}, the authors achieved better results when $G$ was conditioned

@@

>>>>

Wtihin the theme of semantic learning and generation, several significant contributions were made during 2016 and 2017.  Pathak, Krahenbuhl, Donahue, Darrell, and Efros successfully used an adversarial approach to inpaint (fill in missing portions of) images with large extents of missing pixel data \cite{pathakCVPR16context}.  Their architecture was based on an encoder-decoder (TBD ref) combined with GAN.  In their approach, the encoder-decoder learns a semantic encoding based on the non-missing portions and attempts to reproduce a whole image based on that semantic encoding.  The `reconstruction loss' is defined in terms of closesness ($L2$) of the filled area to the removed area. The encoder-decoder is regarded as $G$, and a new Discriminator $D$ is trained to predict whether its input is a reconstructed output from $G$ or an original image.  Interestingly, and in contrast with \cite{mirza2014conditional}, the authors achieved better results when $G$ was conditioned

@@

semantics discovery (semantics of security)
